%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Takashi Henry Idobe} % Your name
\address{27 Melcher St, Boston, MA 02210} % Your address
\address{mail@takashiidobe.com \\ https://takashiidobe.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
Software Development Engineer @ Amazon with 3+ years full-stack experience.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Amazon}{June 2021 - Present}{Software Development Engineer}{Boston, Massachusetts}
\item Technologies used: Typescript, React.js, Java 
\item Built data ingestion and transformation pipelines filtering millions of records a month.
\item Designed microfrontend dashboards to report and visualize millions of records.
\item Wrote and reviewed design documentation to remove redundant functionality from repositories.
\end{rSubsection}

\begin{rSubsection}{CardFlight}{Aug 2019 - June 2021}{Software Engineer II}{Lincoln, Nebraska}
\item Technologies used: Ruby, Typescript, MySQL
\item Expanded line of terminal products, adding features and fixing bugs.
\item Led initiative to implement Level III transactions on payments gateway. 
\item Wrote on-call documentation and improved monitoring for payments gateway.
\end{rSubsection}

\begin{rSubsection}{Savvy}{Mar 2019 - June 2019}{Software Engineer}{Remote}
\item Technologies used: React.js, Redux, Node.js
\item Increased accessibility of product to meet level A ADA compliance.
\item Refactored codebase to decrease load time of app by 40\%.
\item Built and introduced tooling to notify developers introducing accessibility violations.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\newline Languages: ECMAScript, Typescript, Python, Ruby, C++, Rust
\newline Libraries/Frameworks: React.js, Ruby on Rails, Redux, Express
\newline Databases: MySQL, Postgres, DynamoDB
\newline Version Control: Git 
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}
{Waseda University}{Sep 2013 - Jul 2017}{B.A. in Global Political Economics}{Tokyo, Japan}
\end{rSubsection}

\end{rSection}
\end{document}
